---
title: "16S rRNA pipeline using DADA2"
author: 'Instructors: Imane Allali'
---

<br/><br/>
 
## <span style="color:green">The dataset</span>
The dataset we will be working are the practice dataset from the [H3ABioNet 16S rDNA diversity analysis SOP](https://h3abionet.github.io/H3ABionet-SOPs/16s-rRNA-1-0.html). The source data can be accessed [here](http://h3data.cbio.uct.ac.za/assessments/16SrRNADiversityAnalysis/practice) but for our purposes it is already on the cluster.

The table below contains the metadata associated with the dog stool samples. There are three dogs which are treated with increased percentage of a compound in their diet: 5 different treatments (0-4, representing an increased percentage of a compound in their diet).


| Sample  | Dog    | Treatment  | Read Counts r1  | Read Counts r2 |
| :-------| :----: | :--------: | :-------------: | ----------:    | 
|  Dog1   | B      | 2          |  118343         | 118343         |
|  Dog2   | G      | 3          |  108679	        | 108679         | 
|  Dog3   | K      | 3          |  101482         | 101482         | 
|  Dog8   | B      | 4          |  108731         | 108731         | 
|  Dog9   | G      | 0          |  109500         | 109500         | 
|  Dog10  | K      | 4          |  79342          | 79342          | 
|  Dog15  | B      | 1          |  131483         | 131483         | 
|  Dog16  | G      | 4          |  114424         | 114424         | 
|  Dog17  | K      | 0          |  99610	        | 99610	         | 
|  Dog22  | B      | 3          |  145029         | 145029         | 
|  Dog23  | G      | 1          |  193158         | 193158         | 
|  Dog24  | K      | 2          |  162487         | 162487         | 
|  Dog29  | B      | 0          |  122776         | 122776         | 
|  Dog30  | G      | 2          |  137315         | 137315         | 
|  Dog31  | K      | 1          |  150613         | 150613         | 

<br/><br/>

## <span style="color:green">Getting Ready</span>
First, we load the <span style="color:blue">dada2</span> package on your RStudio. if you do not already have it, see the [dada2 installation instructions](https://benjjneb.github.io/dada2/dada-installation.html).

```{r}
library(dada2); packageVersion("dada2")
```


We set the path so that it points to the extracted directory of the dataset named "dog_samples" on your computer or cluster:

```{r}
MY_HOME <- Sys.getenv("HOME")
data <- paste(MY_HOME, "/dada2_tutorial_dog/dog_samples", sep='')  # change the path
list.files(data)
```
